Results

### 2022-07-25 article/results.Rmd
ideas ATBC
add clean varData cols, draft fig1f

```{r setupRes, echo = F, message = F, warning=F, results='hide'}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
source(here::here("figs/fig2.R")); here::i_am("article/results.Rmd"); 
options(digits = 1)
```

@@

Aboveground biomass did not tend to change with distance to primary forest edge 
(Fig \@ref(fig:biomass)a), despite significant trends with underlying related variables 
(Fig \@ref(fig:biomass)).
Median plot wood density tended to increase marginally significantly 
(`r glue("p=",round(as.numeric(wd$pval),3))`) 
with edge distance by 
`r wd$statPrint[[1]]$estimate[[2]]` ± 
`r wd$statPrint[[1]]$std.error[[2]]` per m 
explaining 
`r "R2x100"`% of variance 
among median distance strata values
(Fig \@ref(fig:biomass)b).
Plot stem density also tended to increase significantly 
(`r glue("p=",round(as.numeric(stems12$pval[[2]][2]),2))`) 
with edge distance but more strongly and non-linearly, by 
~`r stems12$statPrint[[1]]$estimate[[2]]` ± 
`r stems12$statPrint[[1]]$std.error[[2]]` per m 
(Fig \@ref(fig:biomass)c).
At this stage in forest regeneration, canopy light availability did not tend to change with distance from forest edge 
(Fig \@ref(fig:biomass)d).

@@

@@

Overall diversity changed significantly with distance to primary forest edge 
(Fig \@ref(fig:taxa)).
Diversity significantly 
(`r glue("p=",round(as.numeric(entropy12$pval[[2]][2]),3))`) 
decreased non-linearly by 
~`r abs(entropy12$statPrint[[1]]$estimate[[2]])` ± 
`r abs(entropy12$statPrint[[1]]$std.error[[2]])` per m 
as distance to primary forest edge increased, 
which explained 
`r "R2x100"`% of variance 
among distance strata medians 
(Fig \@ref(fig:taxa)a) -- 
while in contrast taxonomic richness increased slightly 
(`r glue("p=",round(as.numeric(richness$pval),3))`) 
and linearly 
by 
`r richness$statPrint[[1]]$estimate[[2]]` ± 
`r richness$statPrint[[1]]$std.error[[2]]` per m 
and had `r "R2x100"`% variance explained 
among distance strata 
(Fig \@ref(fig:taxa)b).
Community composition and beta diversity also changed significantly 
(`r glue("p=",ordStat[[5]][1])`) with 
`r ordStat$R2[1] *100`% 
variance among distance strata explained by distance to primary forest edge, 
and the first two principal components explaining 
`r ordTbl$PC1_prop[1] *100`% and 
`r ordTbl$PC2_prop[1] *100`% totaling 
`r (ordTbl$PC1_prop[1] + ordTbl$PC2_prop[1]) *100`% 
of variance among calculated plot distances 
(Fig \@ref(fig:taxa)d).
Key abundant taxa *`r measure2e`* and *`r measure2f`* showed different responses -- *`r measure2e`* nearly tended to decrease with distance to primary forest edge 
(Fig \@ref(fig:taxa)e),
while *`r measure2f`* decreased marginally significantly 
(`r glue("p=",round(as.numeric(ficus$pval),3))`) 
and linearly by 
`r ficus$statPrint[[1]]$estimate[[2]]` ± 
`r ficus$statPrint[[1]]$std.error[[2]]` per m 
with `r "R2x100"`% variance among distance strata explained 
(Fig \@ref(fig:taxa)f).

@@

>>>>

```{r setupRes, echo = F, message = F, warning=F, results='hide'}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
source(here::here("figs/fig2.R")); here::i_am("article/results.Rmd"); 
options(digits = 1)
# source(here::here("figs/fig2.R"));
```

@@

Aboveground biomass did not tend to change with distance to primary forest edge 
(Fig \@ref(fig:biomass)a), despite significant trends with underlying related variables 
(Fig \@ref(fig:biomass)).
Median plot wood density tended to increase marginally significantly 
(`r glue("p=",round(as.numeric(wd$pval),3))`) 
with edge distance by 
`r wd$statPrint[[1]]$estimate[[2]] %>% p_round()` ± 
`r wd$statPrint[[1]]$std.error[[2]] %>% rstatix::p_round()` per m 
explaining 
*`r "~10"`*% of variance 
among median distance strata values
(Fig \@ref(fig:biomass)b).
Plot stem density also tended to increase significantly 
(`r glue("p=",round(as.numeric(stems12$pval[[2]][2]),2))`) 
with edge distance but more strongly and non-linearly, by 
~`r stems12$statPrint[[1]]$estimate[[2]]` ± 
`r stems12$statPrint[[1]]$std.error[[2]]` per m 
(Fig \@ref(fig:biomass)c).
At this stage in forest regeneration, canopy light availability did not tend to change with distance from forest edge 
(Fig \@ref(fig:biomass)d).

@@

<!-- - size distributions? -->
<!-- - put light-biomass correlation? -->

@@

Overall diversity changed significantly with distance to primary forest edge 
(Fig \@ref(fig:taxa)).
Diversity significantly 
(`r glue("p=",round(as.numeric(entropy12$pval[[2]][2]),3))`) 
decreased non-linearly by 
~`r abs(entropy12$statPrint[[1]]$estimate[[2]])` ± 
`r abs(entropy12$statPrint[[1]]$std.error[[2]])` per m 
as distance to primary forest edge increased, 
which explained 
*`r "73"`*% of variance 
among distance strata medians 
(Fig \@ref(fig:taxa)a) -- 
while in contrast taxonomic richness increased slightly 
(`r glue("p=",round(as.numeric(richness$pval),3))`) 
and linearly 
by 
`r richness$statPrint[[1]]$estimate[[2]]` ± 
`r richness$statPrint[[1]]$std.error[[2]]` per m 
and had *`r "16"`*% variance explained 
among distance strata 
(Fig \@ref(fig:taxa)b).
Community composition and beta diversity also changed significantly 
(`r glue("p=",ordStat[[5]][1])`) with 
`r ordStat$R2[1] *100`% 
variance among distance strata explained by distance to primary forest edge, 
and the first two principal components explaining 
`r ordTbl$PC1_prop[1] *100`% and 
`r ordTbl$PC2_prop[1] *100`% totaling 
`r (ordTbl$PC1_prop[1] + ordTbl$PC2_prop[1]) *100`% 
of variance among calculated plot distances 
(Fig \@ref(fig:taxa)d).
Key abundant taxa *`r measure2e`* and *`r measure2f`* showed different responses -- *`r measure2e`* nearly tended to decrease with distance to primary forest edge 
(Fig \@ref(fig:taxa)e),
while *`r measure2f`* decreased marginally significantly 
(`r glue("p=",round(as.numeric(ficus$pval),3))`) 
and linearly by 
`r ficus$statPrint[[1]]$estimate[[2]]` ± 
`r ficus$statPrint[[1]]$std.error[[2]]` per m 
with *`r "~20"`*% variance among distance strata explained 
(Fig \@ref(fig:taxa)f).

@@

<!-- - put diversity-biomass correlation -->
